Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-04 ms.tex
wrote a conclusions section.

\shorttitle{KIC 12557548 b back to normal}
\shortauthors{Schlawin et al.}

@@

>>>>

\shorttitle{KIC 12557548 b back to ``normal''}
\shortauthors{Schlawin et al.}

@@

We obtained ground-based R band photometry from the Kuiper 61-inch observatory to follow up a possible slowdown in disintegration activity observed in 2013 and 2014.
\citet{schlawin2016kic1255} found shallow transits (all below the Kepler observatory average) in August-September 2013 and August-September 2014.
One possibility was a long term evolution of the disintegration activity, such as a reduction of available dusty material of the planet or a slowdown in the disintegration mechanism.
Our transit depths from June-July 2016 are instead consistent with the depths from the Kepler observatory from 2009 to 2013, with a KS-test between the two distributions having a p-value of 0.5 that depths are drawn from the same distribution.
This indicates that the shallow transit depths observed in August-September 2013 and August-September 2014 likely fell into the 14-36 day long quiescent intervals of disintegration activity as observed in Kepler photometry \citep{kawahara2013starspots,vanWerkhoven2014,croll2015starspots}.

We re-analyze the existing Kepler photometry with PCA to better understand the time dependence and statistics of the light curves.
We find that the first eigenvector corresponds to models with small sized dust grains whereas the second eigenvector corresponds to models with large-sized dust grains with larger forward scattering.
The first principal component tracks closely with the transit depths and exhibits modulations at periods of 22.9, 153 and 750 days.
The second principal component is nearly sinusoidal with a 491 day period, indicating possible long term evolution of the dust particle sizes.
The 22.9 day period matches the rotation period of the host star, which has previously been used to tie disintegration to stellar activity \citep{kawahara2013starspots} or occultations of star spots \citep{croll2015starspots}.
The remaining periodicities are longer than the dynamical and sublimation times of the planet and grains, so a different mechanisms would be required to modulate the activity over these timescales.

\citet{vanlieshout2016kic1255} compile the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.
We explore this possibility by examining archival Subaru HDS spectra of \shStar\.
We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T=4500 $\pm$ 110 K, log(g) = 4.5, [Fe/H]=-0.1$\pm$0.1, M=0.7$\pm$0.1 R$_\odot$ and M=0.7 $\pm$0.1 M$_\odot$.
Therefore, the optical depth of any gas sublimating of dust grains is too small to affect the high resolution spectrum.
We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.
